---
title: "Using Aracne"
author: "Juan A. Botía"
date: "30/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This is a set of instructions to use Aracne-AP, introduced here <https://github.com/califano-lab/ARACNe-AP>. You can use it directly from Java or you can use it from R. I have prepared this code here so you can directly use it from R.

You will need to have Java 8 or greater so you can run Aracne. The link above explains how to build Aracne at your machine if you already have Java and Ant (an utility that helps you compile Java software). But if you are lucky, you could try your luck by just downloading my Aracne Jar (Java executable) file and see whether it works.
You can get it from here <https://www.dropbox.com/s/a8zfpymj1ri877a/Aracne.jar?dl=0>.

The R function I have prepared for you is called `runAracneMIJava()` and it implements the call to the Java version of Aracne so you don´t have to learn any Java for using it. The source code appears below. Please feel free to copy it and use it into your own scripts. It is just intended to be an example on how to use Arace from R.
It needs a series of files to work with, and a series of paths. We are using the Aracne-AP version of the software, which is very efficient but also implemented in Java, so you will have to install the Java Virtual Machine first. Normally, all computers have Java installed as it is needed for a lot of things. In case you have problems finding Java, just open a Shell terminal and type `java`. If you can´t run that command, you can get it from here <https://www.java.com/en/download/>.

# The R wrapper to Aracne
There are two functions which basically allow you to indicate where is each Java element (the virtual machine and the Arance software) that you need. The `gjp()` function returns the full path to the executable file of the Java virtual machine. The virtual machine is usually available for all users of the system so it will be installed in some general place, like `/usr/bin/java`. Aracne is the Java based software you will be using and normally you will install it under your path, so we use `gsp()` for that. I have it installed under a `soft` folder, i.e. `/Users/juanbot/soft/aracne/`.
```{r}
gjp = function(){ return("/usr/bin/java")}
gsp = function(){ return("~/NSL_PD_relationships/docs/ARACNe/")}
```

And then comes the main software. These are the basic parameters: 

* `exp.file` : the expression file in the form aracne needs it. Samples are at columns, genes are at rows. The 1st column of the expression file is named `gene` and it contains the name of the corresponding gene at each row. The rest of columns are named with the samples IDs. See an example here <https://www.dropbox.com/s/qnpbjcgmqkbxqpc/SNIG.expr.txt?dl=0>.

* `out.folder`: all results will be saved here

* `tfs.file`: the list of possible regulators (they are seen as transcription factors here, hence the name), just a list of genes, with a gene in each row. See an example here <https://www.dropbox.com/s/uemp19jlw6g94p7/eqtl.SNIG.anchors.txt?dl=0>. Note that genes must be named with the same naming scheme here and at the expression file.

* `p.value`: Aracne gets a significance p-value for each possible interaction between regulator genes and regulated genes. This is a threshold for identifying significant interactions.

* `seed`: the algorithm is based on a random initialization, therefore you will need a `seed` value for guaranteeing results reproducibility. If you want a bootstrapped network, you will need a different seed for each network. Let´s say you want to run Aracne 1000 times and then aggregate the results, for the sake of accuracy. You will need to provide 1000 different seeds (e.g. `1:1000` would do that). The software will detect this, run Aracne 1000 times and then aggregate the results into a final regulon set.

* `calc.threshold`: set this to TRUE always, it says Aracne to automatically calculate what level of `correlation` is good to consider it relevant.

* `tissue` and `which.one`: just for an appropriate naming of the output files, use it to organise your file names accordingly if you have to run it many times or over different tissues/conditions.

```{r}
runAracneMIJava = function(exp.file="~/NSL_PD_relationships/data/ARACNe/SNIG.expr.txt",
		out.folder="~/NSL_PD_relationships/data/ARACNe/",
		tfs.file="~/NSL_PD_relationships/data/ARACNe/eqtl.SNIG.anchors.txt",
		p.value="1E-8", 
		seed=12345,
		calc.threshold=T,
		tissue="SNIG",
		which.one="exonic")
{
	command = paste0(gjp()," -jar ",gsp(),"/Aracne.jar -e ",exp.file," -o ", out.folder,
			" --tfs ",tfs.file," --pvalue ",p.value," --seed ")
	if(calc.threshold){
		init.command = paste0(command,seed[1]," --calculateThreshold")
		cat("Running command\"",init.command,"\"\n")
		system(init.command)
	}
	
	if(length(seed) == 1){
		command = paste0(command,seed," --nobootstrap")
		cat("Running command\"",command,"\"\n")
		system(command)
		out.file = paste0(out.folder,"/",tissue,".",which.one,".aracnet.txt")
		command = paste0("mv ",out.folder,"/nobootstrap_network.txt ",out.file)
		cat("Running command\"",command,"\"\n")
		system(command)
		
		return(read.delim(out.file))
	}
	
	for(single.seed in seed){
		local.command = paste0(command,single.seed)
		cat("Running command\"",local.command,"\"\n")
		system(local.command)	
	}
	command = paste0(gjp()," -jar ",gsp(),"/Aracne.jar -o ", out.folder,
			" --consolidate")
	cat("Running command\"",command,"\"\n")
	system(command)	
	file.remove(list.files(path=out.folder,pattern="bootstrapNetwork_*",full.names=T))
	out.file = paste0(exp.file,".aracnet.txt")
	command = paste0("mv ",out.folder,"/network.txt ",
			out.file)
	cat("Running command\"",command,"\"\n")
	system(command)
	return(read.delim(out.file))
	
}
```

As an example, we can just run it with my default values
```{r}
myresult = runAracneMIJava(exp.file="~/NSL_PD_relationships/data/ARACNe/SNIG.expr.txt",
                           out.folder="~/NSL_PD_relationships/data/ARACNe/",
                           tfs.file="~/NSL_PD_relationships/data/ARACNe/eqtl.SNIG.anchors.txt",
                           p.value="1E-8", 
                           seed=12345,
                           calc.threshold=T,
                           tissue="SNIG",
                           which.one="exonic")
```

And you see when you inspect the results, each row represents a potential interaction between a regulator (i.e. the `Regulator` column) and a regulated gene (i.e. the `Target` column). The MI (Mutual information) refers to the strength of the association between the two.
```{r}
knitr::kable(head(myresult), 
             caption="Results from calling Aracne on a expression dataset with 835 potential transcription factors")
```

